Analysis-ready VCF at Biobank scale using Zarr

### 2025-01-23 paper.tex
Add lungfish as example of large genome

A similar limitation is imposed by the VCF POS field which is encoded
in 32-bit format and can hold chromomosomes up to 2.14 Gbp. Although
spruce does not have chromosomes that exceed the limit, other species
do, such as the recently sequence mistletoe, with chromosomes larger
than 8 Gbp~\cite{dtol_mistletoe}. Zarr's flexible type 
system means that coordinates can be stored as 64 or 32 bit integers
as needed, and there is therefore no particular limit on genome size.
% limitation, and the coordinate system could easily be converted to
% true genome coordinates for storage in Zarr. This updating procedure
% could be applied to any species of choice.

>>>>

A similar limitation is imposed by the VCF POS field which is encoded
in 32-bit format and can hold chromomosomes up to 2.14 Gbp. Although
spruce does not have chromosomes that exceed the limit, other species
do, such as the 87.2 Gbp South American lungfish, whose 19 chromosomes
are all but one larger than the 3.1 Gbp human
genome~\cite{schartl_GenomesAllLungfish_2024}. Zarr's flexible type
system means that coordinates can be stored as 64 or 32 bit integers
as needed, and there is therefore no particular limit on genome size.
% limitation, and the coordinate system could easily be converted to
% true genome coordinates for storage in Zarr. This updating procedure
% could be applied to any species of choice.
